Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-17 paper.qmd
Added text to supplementary section
Added description to the True model

To illustrate the method, we use $7\text{-}D$ simulated data, which we call the "S-curve". It is constructed by simulating $n=750$ observations from $\theta \sim U(-3\pi/2, 3\pi/2)$, $X_1 = \sin(\theta)$, $X_2 \sim U(0, 2)$ (adding thickness to the S), $X_3 = \text{sign}(\theta) \times (\cos(\theta) - 1)$. The remaining variables $X_4, X_5, X_6, X_7$ are all uniform error, with small variance. We would consider $T=(X_1, X_2, X_3)$ to be the geometric structure (true model) that we hope to capture.

@@

>>>>

To illustrate the method, we use $7\text{-}D$ simulated data, which we call the "non-linear clusters". It is constructed by simulating $n=2000$ observations from $\theta \sim U(-3\pi/2, 0)$, $X_1 = \sin(\theta)$, $X_2 \sim U(0, 2)$ (adding thickness to the C), $X_3 = \text{sign}(\theta) \times (\cos(\theta) - 1)$. The remaining variables $X_4, X_5, X_6, X_7$ are all uniform error, with small variance. We would consider $T=(X_1, X_2, X_3)$ to be the geometric structure (true model) that we hope to capture.

@@

Direct links to videos for viewing online are available in .
